Linking hypothesis and number of response options modulate inferred scalar implicature rate

### 2018-11-02 manuscript.tex
resubmission draft

    Correspondence concerning this article should be addressed to Masoud
    Jasbi, Margaret Jacks Hall, Building 460 Rm. 127, Stanford, CA,
    94305-2150. E-mail:
    \href{mailto:masoud_jasbi@fas.harvard.edu}{\nolinkurl{masoudj@stanford.edu}}
  }

@@

In the quaternary task (Figure \ref{fig:quaternaryPlot}), participants
were again at or close to ceiling in responding \enquote{right} and
\enquote{wrong} on 4 of the 6 unambiguously true and false trials.
However, with four response options, two of the control conditions
appear to be showing signs of pragmatic infelicity: when a conjunction
was used and only one of the animals was on the card, participants
considered the guess \enquote{wrong} most of the time, but they often
considered it \enquote{kinda wrong} or even \enquote{kinda right}. This
suggests that perhaps participants considered the notion of a partially
true or correct statement in our experimental setting. Disjunctive
descriptions of cards with only one animal, while previously at ceiling
for \enquote{right} responses, were downgraded to only \enquote{kinda
right} 26\% of the time, presumably because these utterances are also
underinformative, though the degree of underinformativeness may be less
egregious than on scalar trials.

>>>>

    Correspondence concerning this article should be addressed to Masoud
    Jasbi, Margaret Jacks Hall, Building 460 Rm. 127, Stanford, CA,
    94305-2150. E-mail:
    \href{mailto:masoud_jasbi@fas.harvard.edu}{\nolinkurl{masoud_jasbi@fas.harvard.edu}}
  }

@@

In the quaternary task (Figure \ref{fig:quaternaryPlot}), participants
were again at or close to ceiling in responding \enquote{right} and
\enquote{wrong} on 4 of the 6 unambiguously true and false trials.
However, with four response options, two of the control conditions
appear to be showing signs of pragmatic infelicity: when a conjunction
was used and only one of the animals was on the card, participants
considered the guess \enquote{wrong} most of the time (46\%), but they often
considered it \enquote{kinda wrong} (32\%) or even \enquote{kinda right} (19\%). This
suggests that perhaps participants considered the notion of a partially
true or correct statement in our experimental setting. Disjunctive
descriptions of cards with only one animal, while previously at ceiling
for \enquote{right} responses, were downgraded to only \enquote{kinda
right} 26\% of the time, presumably because these utterances are also
underinformative, though the degree of underinformativeness may be less
egregious than on scalar trials.
